\renewcommand{\refname}{Referencias}
\begin{thebibliography}{99}

\bibitem{visi} Sotera Wireless, ViSi Mobile\textregistered  System, rev. 05 marzo 2018, \hyperref[visi]{http://www.soterawireless.com/visi-mobile/}

\bibitem{visi_tel} Sotera Wireless, ViSi Mobile\textregistered  System, rev. 15 Mayo 2018, \hyperref[visi_tel]{https://newatlas.com/visi-mobile-wireless-health-monitoring/25583/}

\bibitem{qardio} Qardio Inc., QardioCore, rev.  05 marzo 2018, \hyperref[qardio]{https://www.getqardio.com/es/qardiocore-wearable-ecg-ekg-monitor-iphone/}

\bibitem{qardio_tel} Qardio Inc., QardioCore, rev.  15 Mayo 2018,
\hyperref[qardio_tel]{https://store.getqardio.com/products/qardiocore}

\bibitem{nuubo} Nuubo, Nuubo wearable ECG, rev. 05 marzo 2018, \hyperref[nuubo]{https://www.nuubo.com/producto}

\bibitem{nuubo_tel} Nuubo, Nuubo wearable ECG, rev. 15 Mayo 2018, \hyperref[nuubo_tel]{http://pdf.medicalexpo.com/pdf/nuubo/necg-minder/83949-96239.html}

\bibitem{ad8232} Analog Devices, ``Single-Lead Heart Rate Monitor Front End'', Rev. B Marzo 2017, \hyperref[ad8232]{http://www.analog.com/media/en/technical-documentation/data-sheets/AD8232.pdf}

\bibitem{RN4020} Microchip, ``Bluetooth Low Energy Module RN4020'', Rev. 15 Mayo 2018, \hyperref[RN4020]{http://ww1.microchip.com/downloads/en/DeviceDoc/50002279B.pdf}

\bibitem{RF} Wikipedia, ``Radio Frecuencia'', Rev. 15 Mayo 2018, \hyperref[RF]{https://es.wikipedia.org/wiki/Radiofrecuencia}

\bibitem{satelite} Wikipedia, ``Comunicaciones por satélite'', Rev. 15 Mayo 2018, \hyperref[satelite]{https://goo.gl/ykf7tv}

\bibitem{wifi} Wikipedia, ``IEEE 802.11'', Rev. 15 Mayo 2018, \hyperref[wifi]{https://goo.gl/1hmiWW}

\bibitem{celular} Wikipedia, ``Red de celdas'', Rev. 15 Mayo 2018, \hyperref[celular]{https://goo.gl/K2sKoQs}

\bibitem{temp} Maxim Integrated, ``Programable Resolution 1-Wire Digital Thermometer'', rev Enero 2015, \hyperref[temp]{https://datasheets.maximintegrated.com/en/ds/DS18B20.pdf}

\bibitem{isp} Microchip, ``In-Circuit Serial Programming (ICSP) Guide'', rev Enero 2015, \hyperref[temp]{http://ww1.microchip.com/downloads/en/devicedoc/30277d.pdf}

\bibitem{ft232} FTDI Chip, ``Future Technology Devices International Ltd. FT232R USB UART IC'', rev 18 noviembre 2015, \hyperref[temp]{http://www.ftdichip.com/Support/Documents/DataSheets/ICs/DS\_ FT232R.pdf}

\bibitem{bateria} Microchip, ``Stand\- Alone System Load Sharing and Li\- Ion Baterry Charge Management Controller'', rev Septiembre 2013, \hyperref[temp]{http://ww1.microchip.com/downloads/en/DeviceDoc/20002090D.pdf}

%
%\bibitem{NETR/NETW} How is data exchanged between two SIMATIC S7-200 %devices in PPI mode?\\
%\hyperref[NETRNETW]{https://support.industry.siemens.com/cs/document/%370000/how-is-data-exchanged-between-two-simatic-s7-200-devices-in-ppi-%mode-?dti=0\&lc=en-WW} 
%
\end{thebibliography}